---
title: <font size="7"><b>Statistical analysis</b></font>
subtitle: <font size="4"><b>Litter decomposition</b> <br> Universidad de Costa Rica</font>
author: <font size="3"><a href="marceloarayasalas.weebly.com/">Marcelo Araya Salas</a> & Andrea Vincent</font>
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    css: extra.css
    df_print: tibble
    highlight: pygments  
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
fontsize: 12pt 
editor_options: 
  chunk_output_type: console
---

<!-- this code add line numbers to code blocks -->
<style>
body
  { counter-reset: source-line 0; }
pre.numberSource code
  { counter-reset: none; }
</style>


<!-- skyblue box -->

<div class="alert alert-info">

# Purpose

- Evaluate role of nutrient availability on litter decomposition

</div>

&nbsp; 

```{r load packages, echo = FALSE, message = FALSE, warning=FALSE}

# remotes::install_github("rlesur/klippy")

# github packages must include user name ("user/package")
pkgs <- c("rlesur/klippy", "kableExtra", "knitr", "readxl", "ggplot2", "tidybayes", "cowplot", "ggrepel", "posterior", "ggridges", "viridis", "brms")

# install/ load packages
sketchy::load_packages(pkgs, quite = TRUE, upgrade.deps = TRUE)
# this is a customized printing for data frames 
# screws up tibble function
tibble <- function(x, ...) { 
  x <- kbl(x, digits=4, align= 'c', row.names = FALSE) 
   x <- kable_styling(x, position ="center", full_width = FALSE,  bootstrap_options = c("striped", "hover", "condensed", "responsive")) 
   asis_output(x)
}

registerS3method("knit_print", "data.frame", tibble)

# this one makes the Rmarkdown found files using the project main folder as it base directory
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(
  class.source = "numberLines lineAnchors", # for code line numbers
  tidy.opts = list(width.cutoff = 65, keep.blank.line=FALSE), # to wrap code
  tidy = TRUE,
  message = FALSE,
  # class.source = "watch-out",
  warning = FALSE,
  message = FALSE
 )

# to add copy button to code blocks
klippy::klippy(position = c('top', 'right'))

```

```{r functions and global parameters, echo = FALSE, message = FALSE, warning=FALSE}

cols <- viridis(10, alpha = 0.7)

# brms models
chains <- 4
iters <- 10000

# set ggplot2 them
ggplot2::theme_set(theme_classic(base_size = 20))


# standard error
se <- function(x) sd(x) / sqrt(length(x))

source("~/Dropbox/R_package_testing/brmsish/R/html_summary.R")
# print results brms models
# html_summary <- function(x, gsub.pattern = NULL, gsub.replacement = NULL, xlab = "Effect size"){
#   
#   summ <- summary(x)$fixed
#   fit <- x$fit  
#   betas <- grep("^b_", names(fit@sim$samples[[1]]), value = TRUE)  
#   hdis <- t(sapply(betas, function(y)   hdi(fit@sim$samples[[1]][[y]]))
# )
#   summ_table <- data.frame(summ, hdis, iterations = attr(fit, "stan_args")[[1]]$iter, chains = length(attr(fit, "stan_args")))
#   summ_table <- summ_table[rownames(summ_table) != "Intercept", c("Estimate", "Rhat", "Bulk_ESS", "l.95..CI", "u.95..CI", "iterations", "chains")]
#   
#   summ_table <- as.data.frame(summ_table)  
#   summ_table$Rhat <- round(summ_table$Rhat, digits = 3)  
#   summ_table$CI_low <- round(unlist(summ_table$l.95..CI), digits = 3)  
#   summ_table$CI_high <- round(unlist(summ_table$u.95..CI), digits = 3)  
#   summ_table$l.95..CI <- summ_table$u.95..CI <- NULL
#   
#     out <- lapply(betas, function(y)  data.frame(variable = y, value = sort(fit@sim$samples[[1]][[y]], decreasing = FALSE)))
#   
#   posteriors <- do.call(rbind, out)
#   posteriors <- posteriors[posteriors$variable != "b_Intercept", ]
#   
#   if (!is.null(gsub.pattern) & !is.null(gsub.replacement))
#     posteriors$variable <- gsub(pattern = gsub.pattern, replacement = gsub.replacement, posteriors$variable)
#   
#    gg <- ggplot(data = posteriors, aes(y = variable, x = value, fill = stat(quantile))) + 
#   geom_density_ridges_gradient(quantile_lines = TRUE, quantile_fun = HDInterval::hdi,  vline_linetype = 2) + 
#   theme_classic() + 
#       labs(x = xlab, y = "Predictor") + 
#      xlim(range(c(min(summ_table[ , "CI_low"]), max(summ_table[ , "CI_high"])), 0)) +
#   geom_vline(xintercept = 0, col = "red") + 
#   scale_fill_manual(values = c("transparent", "#21908C4D", "transparent"), guide = "none") + ggtitle(x$formula)
# 
#   if (!is.null(gsub.pattern) & !is.null(gsub.replacement))
#     rownames(summ_table) <- gsub(pattern = gsub.pattern, replacement = gsub.replacement, rownames(summ_table))
#    
#   summ_table$Rhat <- ifelse(summ_table$Rhat > 1.05, cell_spec(summ_table$Rhat, "html", color ="white", background = "red", bold = TRUE,  font_size = 12),  cell_spec(summ_table$Rhat, "html"))
#   
#   signif <- summ_table[,"CI_low"] * summ_table[,"CI_high"] > 0
#   
#   df1 <- kbl(summ_table, row.names = TRUE, escape = FALSE, format = "html", digits = 3)
#     
#   df1 <- row_spec(kable_input = df1,row =  which(summ_table$CI_low * summ_table$CI_high > 0), background = adjustcolor(cols[9], alpha.f = 0.3))
# 
#   df1 <- kable_styling(df1, bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, font_size = 12)
#   
#   print(df1)
#   
#   print(gg)
# 
# }


```


# Read data

## Nutrient change

### Nitrogen 

Content
```{r}

nutr <- read.csv("./data/raw/litter-nutrients-mas.csv")

nutr$plot.f <- as.factor(nutr$plot)

nutr$days.sc <- scale(nutr$days)

nutr$litter.n.content.prop.initial <- nutr$litter.n.content.perc.initial / 100

# remove plot 9
sub.nutr <- nutr[nutr$plot != 9, ]

agg_n <- aggregate(litter.n.content.perc.initial ~ colecta + treat + days, nutr, mean)

agg_n$sd <- aggregate(litter.n.content.perc.initial ~ colecta + treat + days, nutr, sd)$litter.n.content.perc.initial

agg_n$se <- aggregate(litter.n.content.perc.initial  ~ colecta + treat + days, nutr, se)$litter.n.content.perc.initial

agg_n$treat <- factor(agg_n$treat, levels = c("C", "N", "P", "NP"))

pd <- position_dodge(15)

ggplot(agg_n, aes(x = days, y = litter.n.content.perc.initial, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = litter.n.content.perc.initial + se, ymin = litter.n.content.perc.initial - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter N content (% initial)", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_n$days),
    labels = unique(agg_n$days)) + theme(legend.position = c(0.9, 0.8))

```

```{r, eval = FALSE}

fit.n <- brm(litter.n.content.prop.initial ~  treat * days.sc + (1 | plot.f), data = nutr, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))


saveRDS(fit.n, "./data/processed/litter.n.content.rem_model.RDS")
```

```{r, results='asis', warning=FALSE}

html_summary(read.file = "./data/processed/litter.n.content.rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

Concentration

```{r}

agg_n <- aggregate(perc.n ~ colecta + treat + days, nutr, mean)

agg_n$sd <- aggregate(perc.n ~ colecta + treat + days, nutr, sd)$perc.n

agg_n$se <- aggregate(perc.n  ~ colecta + treat + days, nutr, se)$perc.n

agg_n$treat <- factor(agg_n$treat, levels = c("C", "N", "P", "NP"))

pd <- position_dodge(15)

ggplot(agg_n, aes(x = days, y = perc.n, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = perc.n + se, ymin = perc.n - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter N concentration (%)", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_n$days),
    labels = unique(agg_n$days)) + theme(legend.position = c(0.3, 0.8)) 

```

```{r, eval = FALSE}

nutr$prop.n <- nutr$perc.n / 100

fit.perc.n <- brm(prop.n ~  treat * days.sc + (1 | plot.f), data = nutr, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit.perc.n, "./data/processed/litter.n.perc_model.RDS")

```

```{r, results='asis'}

html_summary(read.file = "./data/processed/litter.n.perc_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```


### Phosphorus 

Content
```{r}

nutr$litter.p.content.prop.initial <- nutr$litter.p.content.perc.initial / 100

# excluding plot 9
agg_p <- aggregate(litter.p.content.perc.initial ~ colecta + treat + days, sub.nutr, mean)

agg_p$sd <- aggregate(litter.p.content.perc.initial ~ colecta + treat + days, sub.nutr, sd)$litter.p.content.perc.initial

agg_p$se <- aggregate(litter.p.content.perc.initial  ~ colecta + treat + days, sub.nutr, se)$litter.p.content.perc.initial


agg_p$treat <- factor(agg_p$treat, levels = c("C", "N", "P", "NP"))


pd <- position_dodge(15)

ggplot(agg_p, aes(x = days, y = litter.p.content.perc.initial, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = litter.p.content.perc.initial + se, ymin = litter.p.content.perc.initial - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter P content (% initial)", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_p$days),
    labels = unique(agg_p$days)) + theme(legend.position = c(0.9, 0.8))

```

```{r, eval = FALSE}

fit.p <- brm(litter.p.content.prop.initial ~  treat * days.sc + (1 | plot.f), data = nutr, chains = chains, iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit.p, "./data/processed/litter.p.content.rem_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/litter.p.content.rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

Concentration

```{r}

agg_p <- aggregate(perc.p ~ colecta + treat + days, sub.nutr, mean)

agg_p$sd <- aggregate(perc.p ~ colecta + treat + days, sub.nutr, sd)$perc.p

agg_p$se <- aggregate(perc.p  ~ colecta + treat + days, sub.nutr, se)$perc.p

agg_p$treat <- factor(agg_p$treat, levels = c("C", "N", "P", "NP"))

pd <- position_dodge(15)

ggplot(agg_p, aes(x = days, y = perc.p, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = perc.p + se, ymin = perc.p - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter P concentration (%)", color = "Treatment")  +
scale_x_continuous(breaks = unique(agg_p$days),
    labels = unique(agg_p$days)) + theme(legend.position = c(0.9, 0.8))

```

```{r, eval = FALSE}

# convert to proportions to use beta distribution
sub.nutr$prop.p <- sub.nutr$perc.p / 100

fit.perc.p <- brm(prop.p ~  treat * days.sc + (1 | plot.f), data = sub.nutr, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit.perc.p, "./data/processed/litter.p.perc_model.RDS")

```

```{r, results='asis'}

html_summary(read.file = "./data/processed/litter.p.perc_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

<div class="alert alert-success">

# Takeaways

- Litter P content is significantly lower in plus N treatment plots than in control plot, after accounting for variation explained by time 

</div>

&nbsp;

Remaining litter 

```{r, eval = TRUE, out.width = "100%", echo = FALSE, fig.align= "center"}

dat <- read_excel("./data/raw/litter_data.xlsx")

dat$plot.f <- as.factor(dat$plot)

dat$prop.litter.rem <- dat$perc.litter.rem / 100

dat$days.sc <- scale(dat$days)

agg_rem <- aggregate(perc.litter.rem ~ colecta + trat + days, dat, mean)

agg_rem$sd <- aggregate(perc.litter.rem  ~ colecta + trat + days, dat, sd)$perc.litter.rem

agg_rem$se <- aggregate(perc.litter.rem  ~ colecta + trat + days, dat, se)$perc.litter.rem

agg_rem <- agg_rem[order(agg_rem$trat), ]

pd <- position_dodge(15)

ggplot(agg_rem, aes(x = days, y = perc.litter.rem, color = trat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = perc.litter.rem + se, ymin = perc.litter.rem - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter mass remaining (%)", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_rem$days),
    labels = unique(agg_rem$days)) + theme(legend.position = c(0.9, 0.8))


```

```{r, eval = FALSE}

fit <- brm(prop.litter.rem ~  trat * days.sc + (1 | plot.f), data = dat, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))


saveRDS(fit, "./data/processed/prop.litter.rem_model.RDS")

dat$days.fc <- as.numeric(as.factor(dat$days))

# monotonic effect of time
fit_mo <- brm(prop.litter.rem ~  trat * mo(days.fc) + (1 | plot.f), data = dat, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_mo, "./data/processed/prop.litter.rem_model_monotonic.RDS")
```

```{r, results='asis'}

html_summary(read.file = "./data/processed/prop.litter.rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

html_summary(read.file = "./data/processed/prop.litter.rem_model_monotonic.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```


Remaining wood 

```{r, eval = TRUE, out.width = "100%", echo = FALSE, fig.align= "center"}

agg_rem_w <- aggregate(perc.wood.rem ~ colecta + trat + days, dat, mean)

agg_rem_w$sd <- aggregate(perc.wood.rem  ~ colecta + trat + days, dat, sd)$perc.litter.rem

agg_rem_w$se <- aggregate(perc.wood.rem  ~ colecta + trat + days, dat, se)$perc.wood.rem

pd <- position_dodge(15)

ggplot(agg_rem_w, aes(x = days, y = perc.wood.rem, color = trat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = perc.wood.rem + se, ymin = perc.wood.rem - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Wood mass remaining (%)", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_rem_w$days),
    labels = unique(agg_rem_w$days)) + theme(legend.position = c(0.9, 0.8)) 


```
&nbsp; 

```{r, eval = FALSE}

dat$prop.wood.rem <- dat$perc.wood.rem / 100

fit2 <- brm(prop.wood.rem ~  trat * days.sc + (1 | plot.f), data = dat, chains = chains, family = Beta(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit2, "./data/processed/prop.wood.rem_model.RDS")
```

```{r, results='asis'}

html_summary(read.file = "./data/processed/prop.wood.rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

# K

## Litter

Correlation between Silvia's and Andrea's K

```{r, eval = TRUE}
k_vals <- read.csv("./data/raw/k-values-corr.csv")

cor(k_vals$av.k.litter, k_vals$sil.k.litter)
cor(k_vals$av.k.wood, k_vals$sil.k.wood)
```

Comparing all treatments vs control

```{r, eval = FALSE}

fit_k.litter <- brm(sil.k.litter ~  Treatment  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.litter, "./data/processed/k_litter_model.RDS")
```

```{r, eval = TRUE, results='asis'}

html_summary(gsub.pattern = "b_treatment|b_", gsub.replacement = "", read.file = "./data/processed/k_litter_model.RDS")

```

Phosphorus vs no-phosphorus
```{r, eval = FALSE}

fit_k.litter.p.np <- brm(sil.k.litter ~  p.treat  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, , control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.litter.p.np, "./data/processed/k_litter_p_nop_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/k_litter_p_nop_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

Nitrogen vs no-nitrogen
```{r, eval = FALSE}

fit_k.litter.n.nn <- brm(sil.k.litter ~  n.treat  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.litter.n.nn, "./data/processed/k_litter_n_no_n_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/k_litter_n_no_n_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

## Wood

Comparing all treatments vs control

```{r}

agg_kvals <- aggregate(sil.k.wood ~ Treatment, k_vals, mean)
agg_kvals$se <- aggregate(sil.k.wood ~ Treatment, k_vals, se)$sil.k.wood
agg_kvals$sd <- aggregate(sil.k.wood ~ Treatment, k_vals, sd)$sil.k.wood

agg_kvals$treat <- factor(agg_kvals$Treatment, levels = c("C", "N", "P", "NP"))

ggplot(k_vals, aes(x = Treatment, y = sil.k.wood)) +
  geom_violin(fill = "#21908C4D") + labs(y = "Decomposition constant (k)") +
  geom_pointrange(data = agg_kvals, aes(ymin = sil.k.wood -se, ymax = sil.k.wood + se))

```

```{r, eval = FALSE}

fit_k.wood.p.treat <- brm(sil.k.wood ~  Treatment  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.wood.p.treat, "./data/processed/k_wood_treatment_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/k_wood_treatment_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

Phosphorus vs no-phosphorus

```{r}

agg_kvals <- aggregate(sil.k.wood ~ p.treat, k_vals, mean)
agg_kvals$se <- aggregate(sil.k.wood ~ p.treat, k_vals, se)$sil.k.wood
agg_kvals$sd <- aggregate(sil.k.wood ~ p.treat, k_vals, sd)$sil.k.wood


agg_kvals$p.treat <- factor(agg_kvals$p.treat, labels = c("No P", "P"))

k_vals$p.treat <- factor(k_vals$p.treat, labels = c("No P", "P"))

ggplot(k_vals, aes(x = p.treat, y = sil.k.wood)) +
  geom_violin(fill = "#21908C4D") + labs(y = "Decomposition constant (k)", x = "P treatment") +
  geom_pointrange(data = agg_kvals, aes(ymin = sil.k.wood -se, ymax = sil.k.wood + se))

```

```{r, eval = FALSE}

fit_k.wood.p.no.p <- brm(sil.k.wood ~  p.treat  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.wood.p.no.p, "./data/processed/k_wood_p_no_p_model.RDS")

```


```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/k_wood_p_no_p_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```


Nitrogen vs no-nitrogen

```{r}

agg_kvals <- aggregate(sil.k.wood ~ n.treat, k_vals, mean)
agg_kvals$se <- aggregate(sil.k.wood ~ n.treat, k_vals, se)$sil.k.wood
agg_kvals$sd <- aggregate(sil.k.wood ~ n.treat, k_vals, sd)$sil.k.wood


agg_kvals$n.treat <- factor(agg_kvals$n.treat, labels = c("No N", "N"))

k_vals$n.treat <- factor(k_vals$n.treat, labels = c("No N", "N"))

ggplot(k_vals, aes(x = n.treat, y = sil.k.wood)) +
  geom_violin(fill = "#21908C4D") + labs(y = "Decomposition constant (k)", x = "N treatment") +
  geom_pointrange(data = agg_kvals, aes(ymin = sil.k.wood -se, ymax = sil.k.wood + se))

```

```{r, eval = FALSE}

fit_k.wood.n.no.n <- brm(sil.k.wood ~  n.treat  + (1 | quadrat), data = k_vals, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_k.wood.n.no.n, "./data/processed/k_wood_n_no_n_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/k_wood_n_no_n_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

# Nutrient content by remaining litter mass

Nitrogen
```{r}

nutr$prom.hoja.reman.sc <- scale(nutr$prom.hoja.reman)

ggplot(data = nutr, aes(x = prom.hoja.reman, y = perc.n, color = treat)) +
  geom_point() + labs(x = "Remaining litter mass (% initial)", y = "Litter N concentration (%)", color = "Treatment") +
  scale_color_viridis_d(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_reverse()

```

```{r, eval = FALSE}

fit_pern_by_rem_leave <- brm(perc.n ~  prom.hoja.reman.sc * treat  + (1 | plot), data = nutr, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_pern_by_rem_leave, "./data/processed/n_per_by_leave_rem_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/n_per_by_leave_rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

Phosphorus

```{r}

ggplot(data = sub.nutr, aes(x = prom.hoja.reman, y = perc.p, color = treat)) +
  geom_point() + labs(x = "Remaining litter mass (% initial)", y = "Litter P concentration (%)", color = "Treatment") +
    scale_color_viridis_d(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_reverse()

```

```{r, eval = FALSE}

fit_perp_by_rem_leave <- brm(perc.p ~  prom.hoja.reman.sc * treat  + (1 | plot), data = sub.nutr, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit_perp_by_rem_leave, "./data/processed/p_per_by_leave_rem_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/p_per_by_leave_rem_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

<!-- light brown box -->

<div class="alert alert-success">

# Takeaways

- Nitrogen percentage, but no Phosphorus percentage, increases along with remaining litter mass 

</div>

&nbsp;

# Nutrient ratios

C:N 
```{r}

# excluding plot 9
agg_cn <- aggregate(cn.mol.kg ~ colecta + treat + days, nutr, mean)

agg_cn$sd <- aggregate(cn.mol.kg ~ colecta + treat + days, nutr, sd)$cn.mol.kg

agg_cn$se <- aggregate(cn.mol.kg  ~ colecta + treat + days, nutr, se)$cn.mol.kg


agg_cn$treat <- factor(agg_cn$treat, levels = c("C", "N", "P", "NP"))


pd <- position_dodge(15)

ggplot(agg_cn, aes(x = days, y = cn.mol.kg, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = cn.mol.kg + se, ymin = cn.mol.kg - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter C:N ratio", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_cn$days),
    labels = unique(agg_cn$days)) + theme(legend.position = c(0.9, 0.8))  

```

```{r, eval = FALSE}

fit.cn <- brm(cn.mol.kg ~  treat * days.sc + (1 | plot.f), data = nutr, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

fit.cn

saveRDS(fit.cn, "./data/processed/cn_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/cn_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

N:P
```{r}

# excluding plot 9
agg_np <- aggregate(np.mol.kg ~ colecta + treat + days, sub.nutr, mean)

agg_np$sd <- aggregate(np.mol.kg ~ colecta + treat + days, sub.nutr, sd)$np.mol.kg

agg_np$se <- aggregate(np.mol.kg  ~ colecta + treat + days, sub.nutr, se)$np.mol.kg


agg_np$treat <- factor(agg_np$treat, levels = c("C", "N", "P", "NP"))


pd <- position_dodge(15)

ggplot(agg_np, aes(x = days, y = np.mol.kg, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = np.mol.kg + se, ymin = np.mol.kg - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter N:P ratio", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_np$days),
    labels = unique(agg_np$days)) + theme(legend.position = c(0.2, 0.8)) 

```

```{r, eval = FALSE}

fit.np <- brm(np.mol.kg ~  treat * days.sc + (1 | plot.f), data = sub.nutr, chains = chains, family = gaussian(), iter = iters, control = list(adapt_delta=0.99, max_treedepth=15))

saveRDS(fit.np, "./data/processed/np_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/np_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```

C:P
```{r}

# excluding plot 9
agg_cp <- aggregate(cp.mol.kg ~ colecta + treat + days, sub.nutr, mean)

agg_cp$sd <- aggregate(cp.mol.kg ~ colecta + treat + days, sub.nutr, sd)$cp.mol.kg

agg_cp$se <- aggregate(cp.mol.kg  ~ colecta + treat + days, sub.nutr, se)$cp.mol.kg

agg_cp$treat <- factor(agg_cp$treat, levels = c("C", "N", "P", "NP"))


pd <- position_dodge(15)

ggplot(agg_cp, aes(x = days, y = cp.mol.kg, color = treat)) +
    geom_point(size= 2, position = pd) + 
    geom_errorbar(aes(ymax = cp.mol.kg + se, ymin = cp.mol.kg - se), width = 0, position = pd) + 
    geom_line(size = 1.2, position = pd) + 
    scale_color_viridis_d(alpha = 0.5) +
    labs(x= "Time (days)", y = "Litter C:P ratio", color = "Treatment") +
scale_x_continuous(breaks = unique(agg_cp$days),
    labels = unique(agg_cp$days)) + theme(legend.position = c(0.9, 0.8)) 

```

```{r, eval = FALSE}

fit.cp <- brm(cp.mol.kg ~  treat * days.sc + (1 | plot.f), data = sub.nutr, chains = chains, family = gaussian(), iter = iters)

fit.cp

saveRDS(fit.cp, "./data/processed/cp_model.RDS")

```

```{r, eval = TRUE, results='asis'}

html_summary(read.file = "./data/processed/cp_model.RDS", gsub.pattern = "b_treatment|b_", gsub.replacement = "")

```
---

&nbsp; 
 
<!-- add packages used, system details and versions  -->
 
<font size="4">Session information</font>

```{r session info, echo=F}

sessionInfo()

```
